GravExplain: Continuous gravitational wave data analysis in a table-top experiment

### 2020-01-21 paper/paper_main.tex
51st day of Summer
53rd day of Summer

\title{GravExplain: Continuous gravitational wave data analysis in the undergraduate laboratory}

@@

\section{Introduction}
\jam{there’s this introduction to the domain context of gravitational waves (which is super awesome) but there’s also basic things about michelson interferometers, do we need to explain that?}

\subsection{Gravitational Waves}
\jam{a previous supervisor hated having subsections right after a section heading, let me know if this displease you as well}

@@

\subsection{Interferometry}
% path difference, virtual thin film interference

\section{Method}

@@

@@

\section{Results and analysis}
% combined/interwoven results, analysis, and discussion

@@

\subsection{Reconstructing music and voice}
% signal processing required
% may well be a ``future work'' section at the end
\jam{! purely hypothetical right now !}

@@

\begin{acknowledgments}
We gratefully acknowledge Jude Prezens, Alex Tolotchkoc, and Blake Molyneux for their technical advice and generous assistance.

J.~Gardner also acknowledges the ANU PhB program for providing travel funding during the project.

@@

>>>>

\title{GravExplain: Continuous gravitational wave data analysis in a table-top experiment}

@@

\section{Introduction}

@@

\section{Method and results}
\jam{a previous supervisor hated having subsections right after a section heading, let me know if this displeases you as well}

\subsection{Hardware: Michelson interferometry}
% path difference, virtual thin film interference

@@

% \section{Results and analysis}
% combined/interwoven results, analysis, and discussion

@@

\subsection{Photodiode viterbi}
\jam{inject simulation wandering tone}

@@

\subsection{Future work: reconstructing music and voice}
% signal processing required
% may well be a ``future work'' section at the end
\jam{! purely hypothetical right now !}

@@

\begin{acknowledgments}
We gratefully acknowledge Jude Prezens, Alex Tolotchkoc, Blake Molyneux, Robin Evans, and Bill Moran for their technical advice and generous assistance throughout the project.

@@

We also acknowledge the ANU PhB program for providing travel funding during the project.
